Deep mutational scanning of an H3 hemagglutinin can inform evolutionary forecasting of human H3N2 influenza virus

### 2017-12-15 paper/manuscript.tex
Added phydms table to results section, changed fig 2 & 3 order

\subsection*{H3 site-specific amino-acid preferences}
How well do the Perth/2009 HA preferences inferred from experimental measurements describe the evolution of H3N2 influenza virus in nature?
\comment{phydms analysis here}

>>>>

\subsection*{H3 site-specific amino-acid preferences}
How well do the Perth/2009 HA preferences inferred from experimental measurements describe the evolution of H3N2 influenza virus in nature?
This question can be addressed by evaluating how well experimentally informed codon substitution models (ExpCM's) constructed from our laboratory measurements improve phylogenetic fit of H3N2 evolution~\citep{hilton2017phydms}.
The results shown in Table~\ref{tab:phydms} show that the ExpCM outperforms conventional substitution models in describing the evolution of human H3N2 HA. 
The ExpCM also optimizes a stringency parameter ($\beta$) for the preferences to more closely reflect the strength of selection in nature.
The stringency parameter in the ExpCM is equal to 2.44, which indicates that although the same amino acids are preferred, the strength of selection is more stringent in nature than in our experiments.
Figure~\ref{fig:logoplot} shows a logo plot of the Perth/2009 HA amino-acid preferences rescaled by this stringency parameter.

\begin{table}
\centering
\begin{tabular}{cccc}
\hline
\bf{Model} & \bf{$\Delta$AIC} & \bf{Log Likelihood} & \bf{Parameters} \\ \hline
ExpCM & 0.0 & -8439.33 & $\beta = 2.44, \kappa = 5.78, \omega = 0.91$ \\
Goldman-Yang M5 & 2166.06 & -9516.36 & $\omega_{\alpha} = 0.30, \omega_{\beta} = 0.84, \kappa = 5.10$ \\
ExpCM, averaged across sites & 2504.18 & -9691.42 & $\beta = 0.68, \kappa = 5.58, \omega = 0.32$ \\
Goldman-Yang M0 & 2607.92 & -9738.29 & $\kappa = 5.05, \omega = 0.31$ \\
\hline
\end{tabular}
\caption{\label{tab:phydms}
{\bf The site-specific amino-acid preferences are informative for describing human H3N2 evolution in nature.}
We implemented several codon substitution models for phylogenetic fitting of an alignment of human H3N2 HA sequences. 
The maximum likelihood values for each model were compared using the Akaike information criteria ($\Delta$AIC)~\citep{posada2004model}.
An experimentally-informed codon substitution model (ExpCM) built from the preferences averaged across all replicates performs better than conventional substitution models, specifically the M0 and M5 models in~\cite{yang2000codon}.
A non-site-specific ExpCM informed by preferences averaged across all sites does not perform as well as the M5 model, but still has a higher log likelihood than M0.
The optimized parameters for each model is also shown.
}
\end{table}
